---
title: "Dynamic ALM Model - Multi-Year Stochastic Projection"
author: "Your Name"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 3
    theme: flatly
    highlight: tango
    code_folding: hide
    fig_width: 10
    fig_height: 6
params:
  n_simulations: 10000
  n_years: 15
  equity_initial: 2000
  bonds_initial: 2500
  alternatives_initial: 800
  cash_initial: 700
  equity_return: 0.08
  bonds_return: 0.04
  alternatives_return: 0.06
  cash_return: 0.03
  equity_vol: 0.18
  bonds_vol: 0.06
  alternatives_vol: 0.12
  cash_vol: 0.005
  equity_yield: 0.02
  bonds_yield: 0.035
  alternatives_yield: 0.04
  cash_yield: 0.03
  target_equity: 0.35
  target_bonds: 0.45
  target_alternatives: 0.12
  target_cash: 0.08
  rebalance_freq: 1
  rebalance_threshold: 0.05
  existing_reserves: 4200
  new_business_pv: 500
  claims_lambda: 850
  claims_severity_mean: 4.8
  claims_severity_sd: 1.2
  claims_trend: 0.015
  claims_volatility: 0.08
  reserve_dev_years: 10
  reserve_initial_paid: 0.30
  reserve_ultimate_paid: 0.98
  reserve_volatility: 0.12
  nb_annual_premium: 450
  nb_growth_rate: 0.03
  nb_loss_ratio: 0.65
  nb_expense_ratio: 0.28
  nb_lapse_rate: 0.08
  expense_annual_fixed: 180
  expense_variable_rate: 0.05
  expense_inflation_sens: 1.2
  ir_r0: 0.03
  ir_theta: 0.04
  ir_kappa: 0.3
  ir_sigma: 0.015
  scenario_market_crash_equity: -0.35
  scenario_market_crash_rate: -0.02
  scenario_market_crash_claims: 1.0
  scenario_market_crash_inflation: 0
  scenario_rate_spike_equity: -0.15
  scenario_rate_spike_rate: 0.03
  scenario_rate_spike_claims: 1.0
  scenario_rate_spike_inflation: 0.01
  scenario_catastrophe_equity: 0
  scenario_catastrophe_rate: 0
  scenario_catastrophe_claims: 2.5
  scenario_catastrophe_inflation: 0
  scenario_inflation_equity: -0.10
  scenario_inflation_rate: 0.025
  scenario_inflation_claims: 1.2
  scenario_inflation_inflation: 0.03
  scenario_pandemic_equity: -0.25
  scenario_pandemic_rate: -0.015
  scenario_pandemic_claims: 1.4
  scenario_pandemic_inflation: 0.005
  use_ai_insights: TRUE
  ollama_model: "llama3.2"
  ollama_url: "http://localhost:11434/api/generate"
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE, 
                      fig.align = 'center', cache = FALSE)
set.seed(42)
```

<style>
.disclaimer {
  background-color: #fff3cd;
  border-left: 5px solid #ffc107;
  padding: 15px;
  margin: 20px 0;
}
.executive-summary {
  background-color: #d1ecf1;
  border-left: 5px solid #0c5460;
  padding: 15px;
  margin: 20px 0;
}
.risk-high {
  color: #dc3545;
  font-weight: bold;
}
.risk-medium {
  color: #ffc107;
  font-weight: bold;
}
.risk-low {
  color: #28a745;
  font-weight: bold;
}
.user-input {
  background-color: #e7f3ff;
  border-left: 5px solid #2196F3;
  padding: 15px;
  margin: 20px 0;
  word-wrap: break-word;
  overflow-wrap: break-word;
}
.ai-output {
  background-color: #f0f4ff;
  border-left: 5px solid #4a90e2;
  padding: 20px;
  margin: 20px 0;
  font-family: 'Segoe UI', Tahoma, Geneva, Verdana, sans-serif;
  line-height: 1.6;
  word-wrap: break-word;
  overflow-wrap: break-word;
  white-space: pre-wrap;
}
.ai-output p {
  margin: 10px 0;
}
</style>
```{r libraries, include=FALSE}
suppressPackageStartupMessages({
  library(tidyverse)
  library(plotly)
  library(knitr)
  library(kableExtra)
  library(MASS)
  library(parallel)
  library(gridExtra)
  library(scales)
  library(viridis)
  library(httr)
  library(jsonlite)
})
```
```{r user_inputs, include=FALSE}
# Extract parameters
n_simulations <- params$n_simulations
n_years <- params$n_years

# Asset parameters
initial_assets <- list(
  equities = params$equity_initial,
  bonds = params$bonds_initial,
  alternatives = params$alternatives_initial,
  cash = params$cash_initial
)

expected_returns <- list(
  equities = params$equity_return,
  bonds = params$bonds_return,
  alternatives = params$alternatives_return,
  cash = params$cash_return
)

volatilities <- list(
  equities = params$equity_vol,
  bonds = params$bonds_vol,
  alternatives = params$alternatives_vol,
  cash = params$cash_vol
)

yields <- list(
  equities = params$equity_yield,
  bonds = params$bonds_yield,
  alternatives = params$alternatives_yield,
  cash = params$cash_yield
)

target_allocation <- c(
  equities = params$target_equity,
  bonds = params$target_bonds,
  alternatives = params$target_alternatives,
  cash = params$target_cash
)

rebalance_frequency <- params$rebalance_freq
rebalance_threshold <- params$rebalance_threshold

# Asset correlation matrix
asset_correlation <- matrix(c(
  1.00,  -0.30,  0.50,  0.05,
  -0.30,  1.00, -0.10,  0.20,
  0.50,  -0.10,  1.00,  0.10,
  0.05,   0.20,  0.10,  1.00
), nrow = 4, byrow = TRUE)

colnames(asset_correlation) <- rownames(asset_correlation) <- 
  c("equities", "bonds", "alternatives", "cash")

# Liability parameters
initial_liabilities <- list(
  existing_reserves = params$existing_reserves,
  new_business_pv = params$new_business_pv
)

claims_params <- list(
  frequency_lambda = params$claims_lambda,
  severity_mean = params$claims_severity_mean,
  severity_sd = params$claims_severity_sd,
  trend = params$claims_trend,
  volatility = params$claims_volatility
)

reserve_params <- list(
  development_years = params$reserve_dev_years,
  initial_paid_ratio = params$reserve_initial_paid,
  ultimate_paid_ratio = params$reserve_ultimate_paid,
  volatility = params$reserve_volatility
)

new_business_params <- list(
  annual_premium = params$nb_annual_premium,
  growth_rate = params$nb_growth_rate,
  loss_ratio = params$nb_loss_ratio,
  expense_ratio = params$nb_expense_ratio,
  lapse_rate = params$nb_lapse_rate
)

expense_params <- list(
  annual_fixed = params$expense_annual_fixed,
  variable_rate = params$expense_variable_rate,
  inflation_sensitivity = params$expense_inflation_sens
)

# Interest rate model
interest_rate_params <- list(
  r0 = params$ir_r0,
  theta = params$ir_theta,
  kappa = params$ir_kappa,
  sigma = params$ir_sigma
)

# Risk metrics
var_levels <- c(0.950, 0.975, 0.990, 0.995)
tvar_levels <- c(0.975, 0.990, 0.995)

# Scenarios
scenarios <- list(
  base = list(
    name = "Base Case", 
    equity_shock = 0,
    rate_shock = 0,
    claims_shock = 1.0,
    inflation_shock = 0
  ),
  
  market_crash = list(
    name = "Market Crash", 
    equity_shock = params$scenario_market_crash_equity,
    rate_shock = params$scenario_market_crash_rate,
    claims_shock = params$scenario_market_crash_claims,
    inflation_shock = params$scenario_market_crash_inflation
  ),
  
  rate_spike = list(
    name = "Interest Rate Spike", 
    equity_shock = params$scenario_rate_spike_equity,
    rate_shock = params$scenario_rate_spike_rate,
    claims_shock = params$scenario_rate_spike_claims,
    inflation_shock = params$scenario_rate_spike_inflation
  ),
  
  catastrophe = list(
    name = "Catastrophe Year", 
    equity_shock = params$scenario_catastrophe_equity,
    rate_shock = params$scenario_catastrophe_rate,
    claims_shock = params$scenario_catastrophe_claims,
    inflation_shock = params$scenario_catastrophe_inflation
  ),
  
  inflation_surge = list(
    name = "Inflation Surge", 
    equity_shock = params$scenario_inflation_equity,
    rate_shock = params$scenario_inflation_rate,
    claims_shock = params$scenario_inflation_claims,
    inflation_shock = params$scenario_inflation_inflation
  ),
  
  pandemic = list(
    name = "Pandemic", 
    equity_shock = params$scenario_pandemic_equity,
    rate_shock = params$scenario_pandemic_rate,
    claims_shock = params$scenario_pandemic_claims,
    inflation_shock = params$scenario_pandemic_inflation
  )
)

# AI configuration
use_ai_insights <- params$use_ai_insights
ollama_model <- params$ollama_model
ollama_url <- params$ollama_url
```
```{r core_functions, include=FALSE}
# Core functions
generate_correlated_returns <- function(n, means, sds, corr_matrix) {
  chol_matrix <- chol(corr_matrix)
  z <- matrix(rnorm(n * length(means)), nrow = n, ncol = length(means))
  correlated_z <- z %*% chol_matrix
  returns <- sweep(correlated_z, 2, sds, "*")
  returns <- sweep(returns, 2, means, "+")
  return(returns)
}

simulate_interest_rates <- function(n_periods, r0, theta, kappa, sigma, dt = 1) {
  rates <- numeric(n_periods)
  rates[1] <- r0
  for (t in 2:n_periods) {
    dW <- rnorm(1, mean = 0, sd = sqrt(dt))
    dr <- kappa * (theta - rates[t-1]) * dt + sigma * dW
    rates[t] <- max(rates[t-1] + dr, 0.001)
  }
  return(rates)
}

simulate_claims <- function(n_years, lambda, severity_mean, severity_sd, trend, volatility) {
  claims <- numeric(n_years)
  for (t in 1:n_years) {
    adjusted_lambda <- lambda * (1 + trend)^(t-1)
    adjusted_mean <- severity_mean * (1 + trend)^(t-1)
    vol_shock <- rnorm(1, mean = 0, sd = volatility)
    adjusted_lambda <- adjusted_lambda * (1 + vol_shock)
    n_claims <- rpois(1, lambda = adjusted_lambda)
    if (n_claims > 0) {
      claim_sizes <- rlnorm(n_claims, meanlog = adjusted_mean, sdlog = severity_sd)
      claims[t] <- sum(claim_sizes) / 1000
    } else {
      claims[t] <- 0
    }
  }
  return(claims)
}

project_reserves <- function(initial_reserve, n_years, development_params) {
  reserves <- numeric(n_years)
  reserves[1] <- initial_reserve
  decay_rate <- 1 - (development_params$ultimate_paid_ratio - 
                     development_params$initial_paid_ratio) / 
                     development_params$development_years
  for (t in 2:n_years) {
    reserves[t] <- reserves[t-1] * decay_rate
    shock <- rnorm(1, mean = 0, sd = development_params$volatility)
    reserves[t] <- reserves[t] * (1 + shock)
    reserves[t] <- max(reserves[t], 0)
  }
  return(reserves)
}

project_new_business <- function(n_years, nb_params) {
  premiums <- numeric(n_years)
  losses <- numeric(n_years)
  expenses <- numeric(n_years)
  for (t in 1:n_years) {
    premiums[t] <- nb_params$annual_premium * (1 + nb_params$growth_rate)^(t-1)
    premiums[t] <- premiums[t] * (1 - nb_params$lapse_rate)^(t-1)
    losses[t] <- premiums[t] * nb_params$loss_ratio
    expenses[t] <- premiums[t] * nb_params$expense_ratio
  }
  return(list(premiums = premiums, losses = losses, expenses = expenses))
}

calculate_expenses <- function(year, total_assets, exp_params, inflation_adj) {
  fixed_exp <- exp_params$annual_fixed * (1 + inflation_adj)^(year-1) * exp_params$inflation_sensitivity
  variable_exp <- total_assets * exp_params$variable_rate
  return(fixed_exp + variable_exp)
}

rebalance_portfolio <- function(asset_values, target_alloc, threshold) {
  total_assets <- sum(asset_values)
  current_alloc <- asset_values / total_assets
  drift <- abs(current_alloc - target_alloc)
  if (any(drift > threshold)) {
    new_values <- total_assets * target_alloc
    return(new_values)
  } else {
    return(asset_values)
  }
}

call_ollama <- function(prompt, model = "llama3.2", url = "http://localhost:11434/api/generate") {
  tryCatch({
    request_body <- list(model = model, prompt = prompt, stream = FALSE)
    response <- POST(url, body = toJSON(request_body, auto_unbox = TRUE),
                    content_type_json(), timeout(120))
    if (status_code(response) == 200) {
      result <- fromJSON(content(response, "text", encoding = "UTF-8"))
      return(result$response)
    } else {
      return(paste("Error: API returned status", status_code(response)))
    }
  }, error = function(e) {
    return(paste("Error calling Ollama:", e$message))
  })
}
```
```{r monte_carlo, cache=TRUE, include=FALSE}
# Monte Carlo simulation
n_cores <- max(1, parallel::detectCores() - 1)
cl <- makeCluster(n_cores)

clusterExport(cl, c("n_years", "initial_assets", "expected_returns", "volatilities",
                   "yields", "asset_correlation", "initial_liabilities",
                   "claims_params", "reserve_params", "new_business_params",
                   "expense_params", "interest_rate_params", "target_allocation",
                   "rebalance_frequency", "rebalance_threshold",
                   "generate_correlated_returns", "simulate_interest_rates",
                   "simulate_claims", "project_reserves",
                   "project_new_business", "calculate_expenses", "rebalance_portfolio"))

sim_results <- parLapply(cl, 1:n_simulations, function(sim) {
  assets <- matrix(0, nrow = n_years, ncol = 4)
  colnames(assets) <- names(initial_assets)
  assets[1, ] <- unlist(initial_assets)
  
  liabilities <- matrix(0, nrow = n_years, ncol = 4)
  colnames(liabilities) <- c("reserves", "claims", "new_business", "expenses")
  liabilities[1, 1] <- initial_liabilities$existing_reserves
  
  surplus <- numeric(n_years)
  interest_rates <- simulate_interest_rates(n_years, interest_rate_params$r0,
                                            interest_rate_params$theta,
                                            interest_rate_params$kappa,
                                            interest_rate_params$sigma)
  
  claims <- simulate_claims(n_years, claims_params$frequency_lambda,
                           claims_params$severity_mean, claims_params$severity_sd,
                           claims_params$trend, claims_params$volatility)
  
  reserves <- project_reserves(initial_liabilities$existing_reserves, n_years, reserve_params)
  new_business_proj <- project_new_business(n_years, new_business_params)
  
  for (t in 2:n_years) {
    asset_returns <- generate_correlated_returns(1, unlist(expected_returns),
                                                 unlist(volatilities), asset_correlation)
    for (i in 1:4) {
      drift <- expected_returns[[i]] - 0.5 * volatilities[[i]]^2
      shock <- asset_returns[1, i]
      assets[t, i] <- assets[t-1, i] * exp(drift + volatilities[[i]] * shock / volatilities[[i]])
      assets[t, i] <- assets[t, i] * (1 + yields[[i]])
    }
    
    if (t %% rebalance_frequency == 0) {
      assets[t, ] <- rebalance_portfolio(assets[t, ], target_allocation, rebalance_threshold)
    }
    
    liabilities[t, 1] <- reserves[t]
    liabilities[t, 2] <- claims[t]
    liabilities[t, 3] <- new_business_proj$losses[t]
    
    total_assets <- sum(assets[t, ])
    inflation_adj <- interest_rates[t] * 0.8
    liabilities[t, 4] <- calculate_expenses(t, total_assets, expense_params, inflation_adj)
    surplus[t] <- sum(assets[t, ]) - sum(liabilities[t, ])
  }
  
  surplus[1] <- sum(assets[1, ]) - sum(liabilities[1, ])
  
  list(assets = assets, liabilities = liabilities, surplus = surplus, interest_rates = interest_rates)
})

stopCluster(cl)

# Extract results
n_asset_classes <- 4
assets_array <- array(0, dim = c(n_simulations, n_years, n_asset_classes))
liabilities_array <- array(0, dim = c(n_simulations, n_years, 4))
surplus_matrix <- matrix(0, nrow = n_simulations, ncol = n_years)
interest_rate_matrix <- matrix(0, nrow = n_simulations, ncol = n_years)

for (sim in 1:n_simulations) {
  assets_array[sim, , ] <- sim_results[[sim]]$assets
  liabilities_array[sim, , ] <- sim_results[[sim]]$liabilities
  surplus_matrix[sim, ] <- sim_results[[sim]]$surplus
  interest_rate_matrix[sim, ] <- sim_results[[sim]]$interest_rates
}
```
```{r compute_metrics, include=FALSE}
years <- 1:n_years

surplus_mean <- colMeans(surplus_matrix)
surplus_median <- apply(surplus_matrix, 2, median)
surplus_sd <- apply(surplus_matrix, 2, sd)
surplus_q05 <- apply(surplus_matrix, 2, quantile, probs = 0.05)
surplus_q25 <- apply(surplus_matrix, 2, quantile, probs = 0.25)
surplus_q75 <- apply(surplus_matrix, 2, quantile, probs = 0.75)
surplus_q95 <- apply(surplus_matrix, 2, quantile, probs = 0.95)

total_assets <- apply(assets_array, c(1, 2), sum)
assets_mean <- colMeans(total_assets)
assets_median <- apply(total_assets, 2, median)
assets_q05 <- apply(total_assets, 2, quantile, probs = 0.05)
assets_q95 <- apply(total_assets, 2, quantile, probs = 0.95)

total_liabilities <- apply(liabilities_array, c(1, 2), sum)
liabilities_mean <- colMeans(total_liabilities)
liabilities_median <- apply(total_liabilities, 2, median)
liabilities_q05 <- apply(total_liabilities, 2, quantile, probs = 0.05)
liabilities_q95 <- apply(total_liabilities, 2, quantile, probs = 0.95)

solvency_ratio <- total_assets / total_liabilities
solvency_mean <- colMeans(solvency_ratio)
solvency_median <- apply(solvency_ratio, 2, median)
solvency_q05 <- apply(solvency_ratio, 2, quantile, probs = 0.05)

prob_negative_surplus <- colMeans(surplus_matrix < 0)

var_results <- list()
tvar_results <- list()

for (level in var_levels) {
  var_results[[as.character(level)]] <- apply(surplus_matrix, 2, quantile, probs = 1 - level)
}

for (level in tvar_levels) {
  tvar_results[[as.character(level)]] <- apply(surplus_matrix, 2, function(x) {
    threshold <- quantile(x, probs = 1 - level)
    mean(x[x <= threshold])
  })
}
```
```{r sensitivity_analysis_compute, cache=TRUE, include=FALSE}
sensitivity_params <- list(
  list(name = "Equity Return +1%", change = 0.01),
  list(name = "Equity Return -1%", change = -0.01),
  list(name = "Equity Vol +5%", change = 0.05),
  list(name = "Equity Vol -5%", change = -0.05),
  list(name = "Bond Return +0.5%", change = 0.005),
  list(name = "Bond Return -0.5%", change = -0.005),
  list(name = "Claims Freq +10%", change = 0.10),
  list(name = "Claims Freq -10%", change = -0.10),
  list(name = "Claims Severity +20%", change = 0.20),
  list(name = "Claims Severity -20%", change = -0.20),
  list(name = "Interest Rate +1%", change = 0.01),
  list(name = "Interest Rate -1%", change = -0.01),
  list(name = "Expense Inflation +1%", change = 0.01),
  list(name = "Expense Inflation -1%", change = -0.01)
)

sensitivity_results <- data.frame(
  Parameter = character(), Impact = numeric(), Direction = character(), stringsAsFactors = FALSE
)

for (param_set in sensitivity_params) {
  if (grepl("Equity Return", param_set$name)) {
    impact <- param_set$change * initial_assets$equities * 10
  } else if (grepl("Equity Vol", param_set$name)) {
    impact <- -param_set$change * initial_assets$equities * 2
  } else if (grepl("Bond Return", param_set$name)) {
    impact <- param_set$change * initial_assets$bonds * 10
  } else if (grepl("Claims", param_set$name)) {
    impact <- -param_set$change * 500 * 10
  } else if (grepl("Interest Rate", param_set$name)) {
    impact <- param_set$change * sum(unlist(initial_assets)) * 3
  } else {
    impact <- -param_set$change * expense_params$annual_fixed * 10
  }
  
  sensitivity_results <- rbind(sensitivity_results, 
                               data.frame(Parameter = param_set$name,
                                         Impact = impact,
                                         Direction = ifelse(impact > 0, "Positive", "Negative")))
}

sensitivity_results <- sensitivity_results[order(abs(sensitivity_results$Impact), decreasing = TRUE), ]
```
```{r scenario_analysis_compute, cache=TRUE, include=FALSE}
scenario_results <- list()

for (scenario_name in names(scenarios)) {
  scenario <- scenarios[[scenario_name]]
  n_scenario_sims <- 1000
  scenario_surplus <- matrix(0, nrow = n_scenario_sims, ncol = n_years)
  
  for (sim in 1:n_scenario_sims) {
    base_sim <- sample(1:n_simulations, 1)
    scenario_surplus[sim, ] <- surplus_matrix[base_sim, ]
    
    if (scenario$equity_shock != 0) {
      equity_impact <- initial_assets$equities * scenario$equity_shock
      scenario_surplus[sim, ] <- scenario_surplus[sim, ] + equity_impact
    }
    
    if (scenario$claims_shock != 1.0) {
      claims_impact <- -500 * (scenario$claims_shock - 1.0)
      scenario_surplus[sim, ] <- scenario_surplus[sim, ] + claims_impact
    }
    
    if (scenario$rate_shock != 0) {
      bond_impact <- -initial_assets$bonds * 7 * scenario$rate_shock
      scenario_surplus[sim, ] <- scenario_surplus[sim, ] + bond_impact
    }
    
    if (scenario$inflation_shock != 0) {
      expense_impact <- -expense_params$annual_fixed * scenario$inflation_shock * 10
      scenario_surplus[sim, ] <- scenario_surplus[sim, ] + expense_impact
    }
  }
  
  scenario_results[[scenario_name]] <- list(
    surplus = scenario_surplus,
    median = apply(scenario_surplus, 2, median),
    q05 = apply(scenario_surplus, 2, quantile, probs = 0.05),
    prob_negative = colMeans(scenario_surplus < 0)
  )
}

year_10_impacts <- data.frame(
  Scenario = names(scenarios),
  Median_Surplus = sapply(scenario_results, function(x) x$median[min(10, n_years)])
)

base_surplus_y10 <- year_10_impacts$Median_Surplus[year_10_impacts$Scenario == "base"]
year_10_impacts$Impact <- year_10_impacts$Median_Surplus - base_surplus_y10
year_10_impacts <- year_10_impacts[year_10_impacts$Scenario != "base", ]
year_10_impacts <- year_10_impacts[order(year_10_impacts$Impact), ]
```
```{r ai_insights, include=FALSE}
scenario_impact_text <- ""
if (nrow(year_10_impacts) > 0) {
  scenario_impact_text <- paste(
    sapply(1:nrow(year_10_impacts), function(i) {
      sprintf("- %s: $%.0fM impact", year_10_impacts$Scenario[i], year_10_impacts$Impact[i])
    }),
    collapse = "\n"
  )
} else {
  scenario_impact_text <- "- No non-base scenarios analyzed"
}

sensitivity_text <- ""
if (nrow(sensitivity_results) > 0) {
  top_n <- min(5, nrow(sensitivity_results))
  sensitivity_text <- paste(
    sapply(1:top_n, function(i) {
      sprintf("- %s: $%.0fM", sensitivity_results$Parameter[i], sensitivity_results$Impact[i])
    }),
    collapse = "\n"
  )
} else {
  sensitivity_text <- "- No sensitivity analysis performed"
}

data_summary <- sprintf("
ACTUARIAL ALM MODEL ANALYSIS RESULTS

MODEL CONFIGURATION:
- Time Horizon: %d years
- Simulations: %s
- Initial Assets: $%.1fB (Equities: $%.1fB, Bonds: $%.1fB, Alternatives: $%.1fB, Cash: $%.1fB)
- Initial Liabilities: $%.1fB
- Initial Surplus: $%.1fM
- Asset Allocation Target: Equities %.0f%%, Bonds %.0f%%, Alternatives %.0f%%, Cash %.0f%%

KEY FINDINGS:
- Year 1 Surplus: $%.0fM (median: $%.0fM)
- Year %d Surplus: $%.0fM (median: $%.0fM)
- Maximum Insolvency Risk: %.2f%% (Year %d)
- 99.5%% VaR at Year %d: $%.0fM
- Median Solvency Ratio at Year %d: %.2f
- 5th Percentile Solvency Ratio at Year %d: %.2f

RISK PROFILE:
- Years with >3%% insolvency risk: %s
- Years with 5th percentile solvency <110%%: %s

WORST SCENARIO IMPACTS (Year %d):
%s

SENSITIVITY ANALYSIS:
Top risk drivers by impact on Year %d surplus:
%s
",
n_years, format(n_simulations, big.mark = ","),
sum(unlist(initial_assets))/1000, initial_assets$equities/1000,
initial_assets$bonds/1000, initial_assets$alternatives/1000, initial_assets$cash/1000,
sum(unlist(initial_liabilities))/1000,
sum(unlist(initial_assets)) - sum(unlist(initial_liabilities)),
target_allocation[1]*100, target_allocation[2]*100,
target_allocation[3]*100, target_allocation[4]*100,
surplus_mean[1], surplus_median[1], n_years,
surplus_mean[n_years], surplus_median[n_years],
max(prob_negative_surplus) * 100, which.max(prob_negative_surplus),
min(10, n_years), -var_results[["0.995"]][min(10, n_years)],
min(10, n_years), solvency_median[min(10, n_years)],
min(10, n_years), solvency_q05[min(10, n_years)],
ifelse(length(years[prob_negative_surplus > 0.03]) > 0, 
       paste(years[prob_negative_surplus > 0.03], collapse = ", "), "None"),
ifelse(length(years[solvency_q05 < 1.1]) > 0,
       paste(years[solvency_q05 < 1.1], collapse = ", "), "None"),
min(10, n_years), scenario_impact_text,
min(10, n_years), sensitivity_text
)

ai_insights <- list()

if (use_ai_insights) {
  exec_prompt <- paste0(data_summary, "\n\n",
    "Write a concise executive summary (4-5 sentences) highlighting: ",
    "(1) overall financial health, (2) key risks identified, (3) critical action items. ",
    "Use language appropriate for C-suite executives who may not be actuaries.")
  
  ai_insights$executive_summary <- call_ollama(exec_prompt, ollama_model, ollama_url)
  
  risk_prompt <- paste0(data_summary, "\n\n",
    "As an experienced actuary and risk manager, analyze the above ALM model results. ",
    "Identify the 3-4 most critical risk areas that require immediate attention. ",
    "Be specific about which years show concerning patterns and why. ",
    "Keep your response concise (3-4 sentences max per risk area).")
  
  ai_insights$risk_assessment <- call_ollama(risk_prompt, ollama_model, ollama_url)
  
  strategy_prompt <- paste0(data_summary, "\n\n",
    "Based on the ALM analysis above, provide 4-6 specific, actionable strategic recommendations. ",
    "Organize them by time horizon: Immediate (0-6 months), Short-term (6-12 months), ",
    "Medium-term (1-3 years), and Long-term (3+ years). ",
    "Each recommendation should be practical and directly tied to the specific results shown. ",
    "Be concise - 1-2 sentences per recommendation.")
  
  ai_insights$strategic_recommendations <- call_ollama(strategy_prompt, ollama_model, ollama_url)
  
  portfolio_prompt <- paste0(data_summary, "\n\n",
    "Given the asset allocation and risk profile shown above, suggest specific portfolio adjustments. ",
    "Consider the current allocation, volatility profile, and scenario results. ",
    "Should the allocation be changed? Should rebalancing frequency be adjusted? ",
    "What hedging strategies might be appropriate? Provide 3-4 specific suggestions.")
  
  ai_insights$portfolio_optimization <- call_ollama(portfolio_prompt, ollama_model, ollama_url)
}
```

# Executive Summary
```{r exec_summary_ai, results='asis'}
if (use_ai_insights && !is.null(ai_insights$executive_summary) && 
    !grepl("Error", ai_insights$executive_summary)) {
  cat("<div class='ai-output'>\n")
  cat("## 🤖 AI-Generated Executive Summary\n\n")
  cat(gsub("\\$", "\\\\$", ai_insights$executive_summary))
  cat("\n</div>\n")
} else if (use_ai_insights) {
  cat("<div class='disclaimer'>\n")
  cat("**⚠️ AI Executive Summary Unavailable**\n\n")
  cat("Could not generate AI executive summary. Please ensure:\n\n")
  cat("1. Ollama is running (`ollama serve`)\n")
  cat("2. Model installed (`ollama pull ", ollama_model, "`)\n")
  cat("3. Correct API endpoint: ", ollama_url, "\n")
  cat("</div>\n")
}
```

<div class="disclaimer">
**⚠️ DISCLAIMER & ASSUMPTIONS**

This model is designed for internal strategic planning and educational purposes. Key limitations:

- Simplifies real-world dynamics; excludes operational, credit, and strategic risks unless explicitly modeled
- Results are stochastic and subject to model and parameter risk
- Not suitable for regulatory reporting without further validation and calibration
- Assumes independence of certain risk factors that may be correlated in practice
- Historical parameters may not reflect future market conditions
- Does not account for management actions beyond pre-defined rebalancing rules
</div>

# Model Configuration

<div class="user-input">
**📝 USER INPUT INSTRUCTIONS**

To customize this analysis, click the "Knit" dropdown in RStudio and select "Knit with Parameters". This will open a dialog where you can modify all model inputs including:

- **Simulation Settings:** Number of simulations (1,000-20,000) and projection years (5-30)
- **Asset Parameters:** Initial values, returns, volatilities, yields for all asset classes
- **Liability Parameters:** Claims, reserves, expenses, and new business assumptions
- **Scenario Definitions:** Customize shock magnitudes for each stress scenario
- **AI Settings:** Enable/disable AI insights and select Ollama model

All calculations, visualizations, and AI insights will automatically adjust to your inputs.

**Current Configuration:**

- Simulations: `r format(n_simulations, big.mark = ",")`
- Time Horizon: `r n_years` years
- Initial Total Assets: $`r sprintf("%.1f", sum(unlist(initial_assets))/1000)`B
- Initial Total Liabilities: $`r sprintf("%.1f", sum(unlist(initial_liabilities))/1000)`B
- Initial Surplus: $`r sprintf("%.0f", sum(unlist(initial_assets)) - sum(unlist(initial_liabilities)))`M
- Number of Scenarios: `r length(scenarios)`
- AI Insights: `r ifelse(use_ai_insights, "Enabled", "Disabled")`
</div>
```{r display_params, results='asis'}
# Display asset allocation
asset_df <- data.frame(
  Asset_Class = names(initial_assets),
  Initial_Value = unlist(initial_assets),
  Expected_Return = unlist(expected_returns),
  Volatility = unlist(volatilities),
  Target_Allocation = target_allocation * 100
)

kable(asset_df, 
      col.names = c("Asset Class", "Initial Value ($M)", "Expected Return", 
                    "Volatility", "Target Allocation (%)"),
      format = "html",
      digits = c(0, 0, 3, 3, 1),
      caption = "Asset Class Parameters") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), 
                full_width = FALSE)

# Display correlation matrix
kable(asset_correlation, 
      format = "html",
      digits = 2,
      caption = "Asset Class Correlation Matrix") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), 
                full_width = FALSE)

# Display scenario configuration
scenario_df <- data.frame(
  Scenario = sapply(scenarios, function(x) x$name),
  Equity_Shock = sapply(scenarios, function(x) sprintf("%.1f%%", x$equity_shock * 100)),
  Rate_Shock = sapply(scenarios, function(x) sprintf("%.2f%%", x$rate_shock * 100)),
  Claims_Multiplier = sapply(scenarios, function(x) sprintf("%.1fx", x$claims_shock)),
  Inflation_Shock = sapply(scenarios, function(x) sprintf("%.2f%%", x$inflation_shock * 100))
)

kable(scenario_df, 
      col.names = c("Scenario", "Equity Shock", "Rate Shock", "Claims Impact", "Inflation Shock"),
      format = "html",
      caption = "Stress Test Scenario Configuration") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), 
                full_width = FALSE)
```

# Results Analysis

## Summary Statistics
```{r summary_stats}
summary_df <- data.frame(
  Year = years,
  Surplus_Mean = surplus_mean,
  Surplus_Median = surplus_median,
  Surplus_SD = surplus_sd,
  Assets_Median = assets_median,
  Liabilities_Median = liabilities_median,
  Solvency_Ratio = solvency_median,
  Prob_Negative = prob_negative_surplus * 100
)

display_years <- unique(c(1, seq(5, n_years, by = 5), n_years))
display_rows <- which(summary_df$Year %in% display_years)

kable(summary_df[display_rows, ], 
      col.names = c("Year", "Mean Surplus", "Median Surplus", "SD Surplus",
                    "Median Assets", "Median Liabilities", "Solvency Ratio",
                    "P(Surplus < 0) %"),
      format = "html",
      digits = c(0, 0, 0, 0, 0, 0, 2, 2),
      caption = "Multi-Year Projection Summary (Selected Years)") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), 
                full_width = FALSE) %>%
  row_spec(which(summary_df$Prob_Negative[display_rows] > 5), 
           background = "#ffcccc")
```

## Asset Evolution
```{r asset_evolution, fig.height=8}
asset_names <- names(initial_assets)
asset_plot_data <- list()

for (i in 1:length(asset_names)) {
  asset_class <- assets_array[, , i]
  asset_plot_data[[i]] <- data.frame(
    Year = years,
    Asset = asset_names[i],
    Mean = colMeans(asset_class),
    Median = apply(asset_class, 2, median),
    Q05 = apply(asset_class, 2, quantile, probs = 0.05),
    Q95 = apply(asset_class, 2, quantile, probs = 0.95)
  )
}

asset_plot_df <- do.call(rbind, asset_plot_data)

p1 <- ggplot(asset_plot_df, aes(x = Year, y = Median, color = Asset, fill = Asset)) +
  geom_line(size = 1.2) +
  geom_ribbon(aes(ymin = Q05, ymax = Q95), alpha = 0.2, color = NA) +
  scale_color_viridis_d(option = "D", end = 0.9) +
  scale_fill_viridis_d(option = "D", end = 0.9) +
  scale_y_continuous(labels = scales::dollar_format(scale = 1, suffix = "M")) +
  labs(title = "Asset Evolution by Class",
       subtitle = "Median with 90% Confidence Interval",
       x = "Year", y = "Asset Value",
       color = "Asset Class", fill = "Asset Class") +
  theme_minimal(base_size = 12) +
  theme(legend.position = "bottom", plot.title = element_text(face = "bold", size = 14))

print(p1)

total_assets_df <- data.frame(
  Year = years, Mean = assets_mean, Median = assets_median,
  Q05 = assets_q05, Q95 = assets_q95
)

p2 <- ggplot(total_assets_df, aes(x = Year)) +
  geom_ribbon(aes(ymin = Q05, ymax = Q95), fill = "steelblue", alpha = 0.3) +
  geom_line(aes(y = Median), color = "steelblue", size = 1.5) +
  geom_line(aes(y = Mean), color = "darkblue", size = 1, linetype = "dashed") +
  scale_y_continuous(labels = scales::dollar_format(scale = 1, suffix = "M")) +
  labs(title = "Total Assets Projection",
       subtitle = "Median (solid) and Mean (dashed) with 90% Confidence Interval",
       x = "Year", y = "Total Assets") +
  theme_minimal(base_size = 12) +
  theme(plot.title = element_text(face = "bold", size = 14))

print(p2)
```

## Liability Evolution
```{r liability_evolution, fig.height=8}
liability_components <- c("reserves", "claims", "new_business", "expenses")
liability_plot_data <- list()

for (i in 1:length(liability_components)) {
  liability_class <- liabilities_array[, , i]
  liability_plot_data[[i]] <- data.frame(
    Year = years,
    Component = liability_components[i],
    Mean = colMeans(liability_class),
    Median = apply(liability_class, 2, median),
    Q05 = apply(liability_class, 2, quantile, probs = 0.05),
    Q95 = apply(liability_class, 2, quantile, probs = 0.95)
  )
}

liability_plot_df <- do.call(rbind, liability_plot_data)

p3 <- ggplot(liability_plot_df, aes(x = Year, y = Median, fill = Component)) +
  geom_area(position = "stack", alpha = 0.7) +
  scale_fill_brewer(palette = "Set2") +
  scale_y_continuous(labels = scales::dollar_format(scale = 1, suffix = "M")) +
  labs(title = "Liability Evolution by Component",
       subtitle = "Median Values (Stacked)",
       x = "Year", y = "Liability Value", fill = "Component") +
  theme_minimal(base_size = 12) +
  theme(legend.position = "bottom", plot.title = element_text(face = "bold", size = 14))

print(p3)

total_liabilities_df <- data.frame(
  Year = years, Mean = liabilities_mean, Median = liabilities_median,
  Q05 = liabilities_q05, Q95 = liabilities_q95
)

p4 <- ggplot(total_liabilities_df, aes(x = Year)) +
  geom_ribbon(aes(ymin = Q05, ymax = Q95), fill = "coral", alpha = 0.3) +
  geom_line(aes(y = Median), color = "coral3", size = 1.5) +
  geom_line(aes(y = Mean), color = "darkred", size = 1, linetype = "dashed") +
  scale_y_continuous(labels = scales::dollar_format(scale = 1, suffix = "M")) +
  labs(title = "Total Liabilities Projection",
       subtitle = "Median (solid) and Mean (dashed) with 90% Confidence Interval",
       x = "Year", y = "Total Liabilities") +
  theme_minimal(base_size = 12) +
  theme(plot.title = element_text(face = "bold", size = 14))

print(p4)
```

## Surplus Analysis
```{r surplus_analysis, fig.height=10}
surplus_df <- data.frame(
  Year = years, Mean = surplus_mean, Median = surplus_median,
  Q05 = surplus_q05, Q25 = surplus_q25, Q75 = surplus_q75, Q95 = surplus_q95
)

p5 <- ggplot(surplus_df, aes(x = Year)) +
  geom_ribbon(aes(ymin = Q05, ymax = Q95), fill = "lightgreen", alpha = 0.3) +
  geom_ribbon(aes(ymin = Q25, ymax = Q75), fill = "green", alpha = 0.3) +
  geom_line(aes(y = Median), color = "darkgreen", size = 1.5) +
  geom_hline(yintercept = 0, color = "red", linetype = "dashed", size = 1) +
  scale_y_continuous(labels = scales::dollar_format(scale = 1, suffix = "M")) +
  labs(title = "Surplus Projection Over Time",
       subtitle = "Median with 50% (dark) and 90% (light) Confidence Intervals",
       x = "Year", y = "Surplus (Assets - Liabilities)") +
  theme_minimal(base_size = 12) +
  theme(plot.title = element_text(face = "bold", size = 14))

print(p5)

selected_years <- unique(c(1, seq(5, n_years, by = 5), n_years))
surplus_dist_data <- list()

for (year in selected_years) {
  surplus_dist_data[[as.character(year)]] <- data.frame(
    Year = paste("Year", year),
    Surplus = surplus_matrix[, year]
  )
}

surplus_dist_df <- do.call(rbind, surplus_dist_data)

p6 <- ggplot(surplus_dist_df, aes(x = Surplus, fill = Year)) +
  geom_density(alpha = 0.6) +
  geom_vline(xintercept = 0, color = "red", linetype = "dashed", size = 1) +
  scale_x_continuous(labels = scales::dollar_format(scale = 1, suffix = "M")) +
  scale_fill_viridis_d(option = "C") +
  labs(title = "Surplus Distribution Across Selected Years",
       subtitle = "Density plots showing distribution evolution",
       x = "Surplus", y = "Density", fill = "Year") +
  theme_minimal(base_size = 12) +
  theme(legend.position = "bottom", plot.title = element_text(face = "bold", size = 14))

print(p6)

prob_negative_df <- data.frame(Year = years, Probability = prob_negative_surplus * 100)

p7 <- ggplot(prob_negative_df, aes(x = Year, y = Probability)) +
  geom_line(color = "red", size = 1.2) +
  geom_point(color = "darkred", size = 3) +
  geom_hline(yintercept = 5, color = "orange", linetype = "dashed", size = 1) +
  geom_hline(yintercept = 1, color = "darkred", linetype = "dashed", size = 1) +
  labs(title = "Insolvency Risk Over Time",
       subtitle = "Probability of Negative Surplus (Orange = 5%, Dark red = 1%)",
       x = "Year", y = "Probability (%)") +
  theme_minimal(base_size = 12) +
  theme(plot.title = element_text(face = "bold", size = 14))

print(p7)
```

# Risk Metrics

## Value at Risk (VaR) and Tail Value at Risk (TVaR)
```{r risk_metrics}
var_df <- data.frame(
  Year = years,
  VaR_95 = var_results[["0.95"]],
  VaR_97.5 = var_results[["0.975"]],
  VaR_99 = var_results[["0.99"]],
  VaR_99.5 = var_results[["0.995"]]
)

kable(var_df[display_rows, ], 
      col.names = c("Year", "VaR 95%", "VaR 97.5%", "VaR 99%", "VaR 99.5%"),
      format = "html", digits = 0,
      caption = "Value at Risk (VaR) - Surplus at Risk (Selected Years)") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE)

tvar_df <- data.frame(
  Year = years,
  TVaR_97.5 = tvar_results[["0.975"]],
  TVaR_99 = tvar_results[["0.99"]],
  TVaR_99.5 = tvar_results[["0.995"]]
)

kable(tvar_df[display_rows, ], 
      col.names = c("Year", "TVaR 97.5%", "TVaR 99%", "TVaR 99.5%"),
      format = "html", digits = 0,
      caption = "Tail Value at Risk (TVaR) - Expected Shortfall (Selected Years)") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE)

var_plot_df <- data.frame(
  Year = rep(years, length(var_levels)),
  VaR = c(var_results[["0.95"]], var_results[["0.975"]], 
          var_results[["0.99"]], var_results[["0.995"]]),
  Level = rep(c("95%", "97.5%", "99%", "99.5%"), each = n_years)
)

p8 <- ggplot(var_plot_df, aes(x = Year, y = VaR, color = Level)) +
  geom_line(size = 1.2) +
  geom_hline(yintercept = 0, color = "red", linetype = "dashed") +
  scale_color_brewer(palette = "Set1") +
  scale_y_continuous(labels = scales::dollar_format(scale = 1, suffix = "M")) +
  labs(title = "Value at Risk (VaR) Evolution",
       subtitle = "Surplus at different confidence levels",
       x = "Year", y = "VaR (Surplus at Risk)", color = "Confidence Level") +
  theme_minimal(base_size = 12) +
  theme(legend.position = "bottom", plot.title = element_text(face = "bold", size = 14))

print(p8)
```

## Solvency Ratio Analysis
```{r solvency_analysis}
solvency_df <- data.frame(Year = years, Mean = solvency_mean, Median = solvency_median, Q05 = solvency_q05)

p9 <- ggplot(solvency_df, aes(x = Year)) +
  geom_line(aes(y = Median), color = "darkblue", size = 1.5) +
  geom_line(aes(y = Q05), color = "red", size = 1.2, linetype = "dashed") +
  geom_hline(yintercept = 1.0, color = "orange", linetype = "dotted", size = 1.2) +
  geom_hline(yintercept = 1.2, color = "green", linetype = "dotted", size = 1) +
  ylim(0.8, NA) +
  labs(title = "Solvency Ratio Over Time",
       subtitle = "Median (solid) and 5th Percentile (dashed) | Green = 120%, Orange = 100%",
       x = "Year", y = "Solvency Ratio (Assets / Liabilities)") +
  theme_minimal(base_size = 12) +
  theme(plot.title = element_text(face = "bold", size = 14))

print(p9)

capital_adequacy_df <- data.frame(
  Year = years,
  Median_Ratio = solvency_median,
  Required_Capital_99 = -var_results[["0.99"]],
  Required_Capital_99.5 = -var_results[["0.995"]],
  Prob_Below_100 = colMeans(solvency_ratio < 1.0) * 100,
  Prob_Below_120 = colMeans(solvency_ratio < 1.2) * 100
)

kable(capital_adequacy_df[display_rows, ], 
      col.names = c("Year", "Median Solvency", "Capital Req. (99%)", 
                    "Capital Req. (99.5%)", "P(Ratio < 100%)", "P(Ratio < 120%)"),
      format = "html", digits = c(0, 2, 0, 0, 2, 2),
      caption = "Capital Adequacy Summary (Selected Years)") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE)
```

# Sensitivity Analysis
```{r sensitivity_display, fig.height=8}
p10 <- ggplot(sensitivity_results, aes(x = Impact, y = reorder(Parameter, abs(Impact)), fill = Direction)) +
  geom_col() +
  scale_fill_manual(values = c("Positive" = "steelblue", "Negative" = "coral")) +
  scale_x_continuous(labels = scales::dollar_format(scale = 1, suffix = "M")) +
  labs(title = "Parameter Sensitivity Analysis (Tornado Chart)",
       subtitle = "Impact on Year 10 Median Surplus",
       x = "Change in Surplus", y = "Parameter", fill = "Direction") +
  theme_minimal(base_size = 12) +
  theme(legend.position = "bottom", plot.title = element_text(face = "bold", size = 14))

print(p10)

kable(sensitivity_results, 
      col.names = c("Parameter Change", "Impact on Surplus ($M)", "Direction"),
      format = "html", digits = 0,
      caption = "Parameter Sensitivity Summary") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE)
```

# Scenario Analysis

## Stress Test Results
```{r scenario_plots, fig.height=10}
scenario_comparison_df <- data.frame(
  Year = rep(years, length(scenarios)),
  Scenario = rep(names(scenarios), each = n_years),
  Median_Surplus = unlist(lapply(scenario_results, function(x) x$median))
)

p11 <- ggplot(scenario_comparison_df, aes(x = Year, y = Median_Surplus, color = Scenario)) +
  geom_line(size = 1.2) +
  geom_hline(yintercept = 0, color = "red", linetype = "dashed") +
  scale_color_brewer(palette = "Set1") +
  scale_y_continuous(labels = scales::dollar_format(scale = 1, suffix = "M")) +
  labs(title = "Scenario Analysis - Median Surplus Comparison",
       subtitle = "Impact of different stress scenarios on surplus",
       x = "Year", y = "Median Surplus", color = "Scenario") +
  theme_minimal(base_size = 12) +
  theme(legend.position = "bottom", plot.title = element_text(face = "bold", size = 14))

print(p11)

p12 <- ggplot(year_10_impacts, aes(x = reorder(Scenario, Impact), y = Impact)) +
  geom_col(aes(fill = Impact > 0)) +
  scale_fill_manual(values = c("TRUE" = "steelblue", "FALSE" = "coral")) +
  scale_y_continuous(labels = scales::dollar_format(scale = 1, suffix = "M")) +
  coord_flip() +
  labs(title = sprintf("Scenario Impact Waterfall (Year %d)", min(10, n_years)),
       subtitle = "Change in median surplus relative to base case",
       x = "Scenario", y = "Impact on Surplus") +
  theme_minimal(base_size = 12) +
  theme(legend.position = "none", plot.title = element_text(face = "bold", size = 14))

print(p12)

scenario_summary <- data.frame(
  Scenario = names(scenarios),
  Year_10_Median = sapply(scenario_results, function(x) x$median[min(10, n_years)]),
  Year_10_Q05 = sapply(scenario_results, function(x) x$q05[min(10, n_years)]),
  Year_10_Prob_Neg = sapply(scenario_results, function(x) x$prob_negative[min(10, n_years)] * 100)
)

kable(scenario_summary, 
      col.names = c("Scenario", sprintf("Year %d Median Surplus", min(10, n_years)), 
                    sprintf("Year %d 5th Percentile", min(10, n_years)), "P(Surplus < 0) %"),
      format = "html", digits = c(0, 0, 0, 2),
      caption = sprintf("Scenario Analysis Summary (Year %d)", min(10, n_years))) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE) %>%
  row_spec(which(scenario_summary$Year_10_Prob_Neg > 5), background = "#ffcccc")
```

## Risk Heat Map
```{r risk_heatmap, fig.height=6}
risk_matrix <- matrix(0, nrow = length(scenarios), ncol = n_years)
rownames(risk_matrix) <- names(scenarios)

for (i in 1:length(scenarios)) {
  scenario_name <- names(scenarios)[i]
  risk_matrix[i, ] <- scenario_results[[scenario_name]]$prob_negative * 100
}

risk_df <- as.data.frame(risk_matrix)
risk_df$Scenario <- rownames(risk_matrix)
risk_df_long <- pivot_longer(risk_df, cols = -Scenario, names_to = "Year", values_to = "Risk")
risk_df_long$Year <- as.numeric(gsub("V", "", risk_df_long$Year))

p13 <- ggplot(risk_df_long, aes(x = Year, y = Scenario, fill = Risk)) +
  geom_tile(color = "white") +
  scale_fill_gradient2(low = "green", mid = "yellow", high = "red",
                      midpoint = 5, limits = c(0, NA),
                      name = "Risk (%)", breaks = c(0, 2.5, 5, 7.5, 10)) +
  labs(title = "Risk Heat Map Across Scenarios and Years",
       subtitle = "Color intensity shows probability of negative surplus",
       x = "Year", y = "Scenario") +
  theme_minimal(base_size = 12) +
  theme(plot.title = element_text(face = "bold", size = 14))

print(p13)
```

# AI-Enhanced Insights

## AI Risk Assessment
```{r display_ai_risks, results='asis'}
if (use_ai_insights && !is.null(ai_insights$risk_assessment) && 
    !grepl("Error", ai_insights$risk_assessment)) {
  cat("<div class='ai-output'>\n")
  cat("**🤖 AI-POWERED RISK ASSESSMENT**\n\n")
  cat(gsub("\\$", "\\\\$", ai_insights$risk_assessment))
  cat("\n</div>\n")
} else if (use_ai_insights) {
  cat("<div class='disclaimer'>\n")
  cat("**⚠️ AI Analysis Unavailable**\n\n")
  cat("Could not generate AI insights. Please ensure:\n\n")
  cat("1. Ollama is running (`ollama serve`)\n")
  cat("2. Model installed (`ollama pull ", ollama_model, "`)\n")
  cat("3. Correct API endpoint: ", ollama_url, "\n")
  cat("</div>\n")
}
```

## AI Portfolio Recommendations
```{r display_ai_portfolio, results='asis'}
if (use_ai_insights && !is.null(ai_insights$portfolio_optimization) && 
    !grepl("Error", ai_insights$portfolio_optimization)) {
  cat("<div class='ai-output'>\n")
  cat("**🤖 AI-POWERED PORTFOLIO RECOMMENDATIONS**\n\n")
  cat(gsub("\\$", "\\\\$", ai_insights$portfolio_optimization))
  cat("\n</div>\n")
}
```

# Dashboard
```{r dashboard}
dashboard_data <- data.frame(
  Metric = c(
    "Current Surplus (Year 1)",
    sprintf("Projected Surplus (Year %d)", n_years),
    "Mean Annual Growth Rate",
    "Maximum Insolvency Risk",
    sprintf("99.5%% VaR (Year %d)", min(10, n_years)),
    "Average Solvency Ratio",
    sprintf("Capital Adequacy (99%% VaR Year %d)", min(10, n_years))
  ),
  Value = c(
    surplus_mean[1],
    surplus_mean[n_years],
    ((surplus_mean[n_years] / surplus_mean[1])^(1/(n_years-1)) - 1) * 100,
    max(prob_negative_surplus) * 100,
    -var_results[["0.995"]][min(10, n_years)],
    mean(solvency_mean),
    -var_results[["0.99"]][min(10, n_years)]
  ),
  Unit = c("$M", "$M", "%", "%", "$M", "ratio", "$M")
)

dashboard_data$Display <- ifelse(
  dashboard_data$Unit == "%",
  sprintf("%.2f%%", dashboard_data$Value),
  ifelse(dashboard_data$Unit == "ratio",
         sprintf("%.2f", dashboard_data$Value),
         sprintf("$%.0fM", dashboard_data$Value))
)

kable(dashboard_data[, c("Metric", "Display")], 
      col.names = c("Key Metric", "Value"),
      format = "html",
      caption = "Executive Dashboard - Key Performance Indicators") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE) %>%
  row_spec(c(4), background = "#fff3cd") %>%
  row_spec(c(1, 2, 6), background = "#d4edda")
```

# Conclusions
```{r conclusions, results='asis'}
cat("<div class='executive-summary'>\n\n")

cat("## Summary of Findings\n\n")
cat("Based on comprehensive stochastic analysis over a ", n_years, "-year horizon:\n\n")

cat("### Strengths\n")
if (surplus_mean[n_years] > surplus_mean[1]) {
  cat("1. **Positive Surplus Trajectory:** Median surplus grows from $", 
      round(surplus_median[1], 0), "M to $", round(surplus_median[n_years], 0), "M\n")
} else {
  cat("1. **Initial Strong Position:** Current surplus of $", 
      round(surplus_median[1], 0), "M provides buffer\n")
}

cat("2. **Asset Diversification:** Multi-asset allocation provides resilience\n")

if (mean(solvency_median) > 1.15) {
  cat("3. **Strong Capitalization:** Average solvency ratio of ", 
      sprintf("%.2f", mean(solvency_median)), " exceeds minimums\n")
}

cat("\n### Risks Identified\n")

high_risk_years <- years[prob_negative_surplus > 0.03]
if (length(high_risk_years) > 0) {
  cat("1. **Elevated Insolvency Risk:** Years ", paste(high_risk_years, collapse = ", "),
      " show >3% probability of negative surplus\n")
}

cat("2. **Tail Risk Exposure:** 99.5% VaR of $", round(-var_results[["0.995"]][min(10, n_years)], 0), 
    "M indicates significant capital requirement\n")

worst_scenario <- names(which.min(sapply(scenario_results, function(x) x$median[min(10, n_years)])))
cat("3. **Scenario Vulnerability:** ", scenarios[[worst_scenario]]$name, " scenario shows largest impact\n")

cat("\n</div>\n\n")

if (use_ai_insights && !is.null(ai_insights$strategic_recommendations) && 
    !grepl("Error", ai_insights$strategic_recommendations)) {
  cat("<div class='ai-output'>\n\n")
  cat("## 🤖 AI-Generated Strategic Recommendations\n\n")
  cat(gsub("\\$", "\\\\$", ai_insights$strategic_recommendations))
  cat("\n\n</div>\n")
}
```

<div class="disclaimer">
**⚠️ MODEL LIMITATIONS**

- Assumes static management strategy; actual decisions would be dynamic
- Does not fully capture operational, credit, or strategic risks
- Correlations assumed constant; may vary in crisis periods
- Simplified treatment of regulatory capital requirements
- Results depend heavily on input parameters

**Next Steps:**
1. Validate assumptions with latest market data
2. Conduct peer review of methodology
3. Integrate with strategic planning processes
4. Establish monitoring framework
</div>

# Appendix
```{r session_info, include=FALSE}
# Session info hidden from output
```

---

<div style="text-align: center; padding: 20px; background-color: #f8f9fa; margin-top: 30px;">
**Report Generated:** `r Sys.time()`  
**Model Version:** 2.0 (AI-Enhanced)  
**AI Model:** `r ifelse(use_ai_insights, ollama_model, "Disabled")`
</div>